---
title: "Untitled"
author: "Beicheng Huang"
date: "2023-09-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1


```{r loading}
library(tidyverse)
library(moderndive)
data("early_january_weather")
weather_data=get("early_january_weather")
```

Description:
colnames(weather_data)
nrow(weather_data)
ncol(weather_data)

Mean of temperature:
mean(weather_data$temp)

Variable names include ([1] "origin"     "year"       "month"      "day"        "hour"       "temp"       "dewp"       "humid"   "wind_dir"   "wind_speed" "wind_gust"  "precip"     "pressure"   "visib"      "time_hour"). There are in total of 358 rows and 15 columns in the "early_january_weather" describing the weather in EWR in Early Jan in 2013.
The mean temperature is 39.58212.


Plots:

```{r plotting}
scatplot <- ggplot(weather_data, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(
    title = "Temperature vs. Time Hour (Colored by Humidity)",
    x = "Time Hour",
    y = "Temperature"
  )

ggsave("Weather plot temperature vs Time.png", plot = scatplot, width = 6, height = 4)


```

Descrpition:
  There's an initial decrease in temperature from 4o followed by fluctuations that gradually increases the temperature to a peak near 60 by Jan.14, ended with a sudden drop in temperature back to around 40.Humidity seems to be modifying the relation where increase in temperatures seems to be related with low humidity and decrease in temperature is related with high humidity.
  
  
##Question 2

```{r }

#Create random sample
set.seed(123)
random_sample <- rnorm(10)

# Create a logical vector indicating whether elements of the sample are greater than 0
logical_vector <- random_sample > 0

# Create a character vector of length 10
character_vector <- c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J")

# Create a factor vector of length 10 with 3 different factor levels
factor_vector <- factor(sample(c("Level1", "Level2", "Level3"), 10, replace = TRUE))

# Create the data frame
my_data_frame <- data.frame(
  RandomSample = random_sample,
  IsGreaterThanZero = logical_vector,
  CharacterVector = character_vector,
  FactorVector = factor_vector
)

mean_random <- mean(pull(my_data_frame, RandomSample))
mean_logical <- mean(pull(my_data_frame, IsGreaterThanZero))
mean_character <- mean(pull(my_data_frame, CharacterVector))
mean_factor <- mean(pull(my_data_frame, FactorVector))

cat("Mean of RandomSample:", mean_random, "\n")
cat("Mean of IsGreaterThanZero:", mean_logical, "\n")
cat("Mean of CharacterVector:", mean_character, "\n")
cat("Mean of FactorVector:", mean_factor, "\n")
```

Description
Mean of RandomSample: 0.07462564 
Mean of IsGreaterThanZero: 0.5 
Mean of CharacterVector: NA 
Mean of FactorVector: NA 
Some of the variables are not numerical and cannot calculate mean.
